Notes for General Relativity

### 2016-09-16 Complex Geometry - index/misc/complex geometry-misc.tex
Solve one minor problem in landau's book. Solved one major step in one problem in complex geometry.

% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures

@@

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
\end{thebibliography}
\printnomenclature

>>>>

        However, I am dubious about this conclusion, since I think it
        needs in addition that the polynomial ring $F[x]$ has not
        nonzero zero divisor.

        Having demonstrated the above simple case, the author continues to
        prove the main theorem. He proves by induction. He first uses:
        \begin{align}
            \left(
                \begin{array}{cc}
                 A & b \\
                 c & d \\
                \end{array}
            \right)  \left(
                \begin{array}{cc}
                 \text{dI} & 0 \\
                 -c & 1 \\
                \end{array}
            \right)=\left(
                \begin{array}{cc}
                 A_0 & b \\
                 0 & d \\
                \end{array}
            \right)
        \end{align}
        where $A,A_0\in \tensor[^{m-1}]{R}{^{m-1}}, 
        b\in \tensor[^{m-1}]{R}{}, c\in \tensor{R}{^{m-1}}, d\in R$. 
        Therefore, (let $M=
            \left(
            \begin{array}{cc}
             A & b \\
             c & d \\
            \end{array}
            \right)$)
        with similar reason mentioned before, he shows if:
        \begin{align}
            \text{det}_F \mathbf{A_0} =
              \text{det}_F \mathbf{( \text{det}_R \mathbf{A_0})}
        \end{align}
        (which is true by induction) then:
        \begin{align}
            \text{det}_F \mathbf{M} =
              \text{det}_F \mathbf{( \text{det}_R \mathbf{M})}
        \end{align}
        Proof completes.

        He also mentions a corollary:
        \begin{coro}
            Let $\mathbf{P}\in \tensor[^n]{F}{^n}$ and $\mathbf{Q}\in
            \tensor[^m]{F}{^m}$, then
            \begin{align}
                \text{det}_F (\mathbf{P\otimes Q}) =
                (\text{det}_F \mathbf{P}) ^m (\text{det}_F \mathbf{Q})^n
            \end{align}
        \end{coro}

        The proof is quite straightforward and is omitted.
        \subsubsection{Why \texorpdfstring{$M_n = \frac{GL(2n,\mathbb{R})}
            {GL(n,\mathbb{C})}$}{} (continued)}

        Coming back to my point. This is a note of my question on
        Math.SE\cite{math.se_3}

        First, I try to do it when $n=1$. I inject a complex number 
        $a+bi$ by
        identify it with $a\mathbb{I}+b\mathbb{J}$, where $\mathbb{I}$ 
        is the identify matrix and $\mathbb{J}$ is
        $ \left(
        \begin{array}{cc}
         0 & -1 \\
         1 & 0 \\
        \end{array}
        \right) $. I take one set of basis of 
        $\mathrm{GL}(2,\mathbb{R})$ as:
        $$
        \left(
        \begin{array}{cc}
         1 & 0 \\
         0 & 1 \\
        \end{array}
        \right),\left(
        \begin{array}{cc}
         0 & -1 \\
         1 & 0 \\
        \end{array}
        \right),\left(
        \begin{array}{cc}
         0 & 0 \\
         1 & 0 \\
        \end{array}
        \right),\left(
        \begin{array}{cc}
         0 & 0 \\
         0 & 1 \\
        \end{array}
        \right)
        $$

        (I think this is a basis because the following matrix is 
        non-singular:
        $$
        \left(
        \begin{array}{cccc}
         1 & 0 & 0 & 0 \\
         0 & -1 & 0 & 0 \\
         0 & 1 & 1 & 0 \\
         1 & 0 & 0 & 1 \\
        \end{array}
        \right)
        $$)
        Then the $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}
        (n,\mathbb{C})}$ becomes equivalent classes represented by 
        $$
        \left(
        \begin{array}{cc}
         0 & 0 \\
         c & d \\
        \end{array}
        \right)
        $$

        However, I don't know how to link this with an almost complex 
        structure.

        I have a feeling that I might have been in the wrong direction. 
        It was pointed out that $\mathrm{GL}(2n,\mathbb{R})$ is not
        even a vector space. So what I did is in fact nonsense.

        Below is one correct answer I got:

        An almost-complex structure is a matrix $J$ such that $J^2 = -I$
        is the negative identity. As you said, one example of such a 
        matrix $J$ is $$\begin{pmatrix} 0 & I \\ -I & 0 \end{pmatrix}.$$

        Interpreting $GL(n,\mathbb{C})$ as a subgroup of 
        $GL(2n;\mathbb{R})$ depends on having fixed such an 
        almost-complex structure. Once we have a matrix $J$, we can call 
        a matrix $A \in GL(2n;\mathbb{R})$ complex-linear if it commutes 
        with $J$, i.e. $AJA^{-1} = J.$

        (The idea is that $\mathbb{C}$-linear maps $T$ are just real 
        linear maps with the additional property that $T(iv) = i T(v)$
        for all vectors $v$)

        Given any matrix $A \in GL(2n;\mathbb{R})$, we get another 
        almost-complex structure $AJA^{-1}$. This is the same 
        almost-complex structure $J$ if and only if 
        $A \in GL(n;\mathbb{C}).$ On the other hand, all almost-complex 
        structures are similar (although it may take some work to be 
        convincing that they are similar over $\mathbb{R}$ and not 
        only $\mathbb{C}$) since they are diagonalizable with the same 
        eigenvalues $\pm i$. That gives you a bijection 
        $$
            GL(2n;\mathbb{R}) / GL(n;\mathbb{C}) \longrightarrow 
            \{\mathrm{almost}-\mathrm{complex}\; 
            \mathrm{structures}\}
        $$ 
        under which a class $A \cdot GL(n;\mathbb{C})$ corresponds 
        to the almost-complex structure $AJA^{-1}.$

        I questioned him:
        \begin{enumerate}
            \item Why $AJA^{-1}$ is the same almost-complex structure 
                $J$ if and only if $A\in \mathrm{GL}(n;\mathbb{C})$. 
            \item Why all almost-complex structures are similar over 
                $\mathbb{R}$.
        \end{enumerate}
        He responsed that:
        \begin{enumerate}
            \item is the definition of $\mathrm{GL}(n;\mathbb{C})$
                as matrices $A$ with $AJA^{-1}=J$.
            \item comes from the fact that any real matrices that are 
                similar over $\mathbb{C}$ are already similar over 
                $\mathbb{R}$. This isn't trivial but it has been asked 
                and answered many times on this site: here is one 
                reference \url{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
        \end{enumerate}

        Inside the reference, the following theorem is proved:

        \begin{thm}
            Let $E$ be a field, let $F$ be a subfield, and let $A$ and
            $B$ be $nxn$ matrices with coefficients in $F$. If $A$ and
            $B$ are similar over $E$, they are similar over $F$.
        \end{thm}
% TODO also, this post may be useful:http://math.stackexchange.com/questions/1400917/equivalence-of-almost-complex-structures

@@

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
  \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
\end{thebibliography}
\printnomenclature

### 2016-09-16 G.R/G.R.tex
Solve one minor problem in landau's book. Solved one major step in one problem in complex geometry.

@@

>>>>

\usepackage{tensor}

@@

    \subsection{Four-vectors}
    \label{sec:Four-vectors}

    This section is basically an recapitulation of important definitions
    and results in tensor analysis in spacetime. Since I am quite
    familiar with this topic, I will only cover something I felt new.

    \paragraph{Complete antisymmetric tensor $e^{iklm}$}
    It is defined such that any interchange of indices gives a minus
    sign. We requires that:
    \begin{align}
        e^{0123}= +1
    \end{align}
    Therefore:
    \begin{align*}
        e_{0123}= -1\;, e^{iklm}e_{iklm}= -24
    \end{align*}
    Also, $e^{iklm}$ is only a pseudotensor:
    \begin{proof}
        Under transformation (let $\Lambda$ be the transformation matrix)
        we have:
        $\tilde{e}^{0123}=
          \Lambda^{0}_{i}\Lambda^{1}_{k}\Lambda^{2}_{l}\Lambda^{3}_{m}
          e^{iklm}$
        Notice that $e^{iklm}=\mathrm{sgn}(iklm)$ by our definition.
        Therefore, the right hand side above is exactly the definition
        of determinant. Hence $\tilde{e}^{0123}=\mathrm{det}(\Lambda)$.

        Also, one can easily show that $\tilde{e}^{nqpr}$ is also
        totally antisymmetric, since $e^{iklm}$ is totally antisymmetric.

        With these we have:
        $$
            \tilde{e}^{nqpr}=\mathrm{det}(\Lambda)e^{nqpr}
        $$
        But $e^{iklm}$ is defined without reference to basis, therefore
        we have actually:
        \begin{align}
            \tilde{e}^{nqpr} \equiv e^{npqr}
        \end{align}
        Note that since $\Lambda$ must be orthonormal, we have 
        $\mathrm{det}(\Lambda)=\pm 1$. Therefore when
        $\mathrm{det}(\Lambda)=1$, the two requirement coincide and
        $e^{iklm}$ behaves like a tensor, and when 
        $\mathrm{det}(\Lambda)=-1$, it behaves like a pseudotensor.
    \end{proof}
